Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-13 paper/manuscript.Rmd
Update neeman reference (it said it was 2009 but in reality it is 2010)

\R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
We thus tested the sensitivity of our approach to two fundamental assumptions. 
First, we tested that visitation is an appropriate proxy to infer interspecific effects by comparing the results obtained using visitation to two alternative metrics in a separate dataset that lacked invasive species [@ballantyne_constructing_2015]. 
Specifically, we also calculated the controllability (the size of the minimum driver node-set) and the control capacity of networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009]. 
\R{R2-sentence-fragment} See Supporting Information Section \@ref(S-visitation-as-proxy) for more details.

@@

\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species' interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009]. 
Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
Indeed, we found strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing the weakest interactions (Supporting Information Section \@ref(S-undersampling)). 
Despite removing rare interactions and species, the relative size of the minimum driver-node set, the superior species, and the relative rankings of control capacity were generally maintained. Of particular note, we found that critical species in the full network were also critical in the vast majority of rarefied networks.

>>>>

\R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
We thus tested the sensitivity of our approach to two fundamental assumptions. 
First, we tested that visitation is an appropriate proxy to infer interspecific effects by comparing the results obtained using visitation to two alternative metrics in a separate dataset that lacked invasive species [@ballantyne_constructing_2015]. 
Specifically, we also calculated the controllability (the size of the minimum driver node-set) and the control capacity of networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2010]. 
\R{R2-sentence-fragment} See Supporting Information Section \@ref(S-visitation-as-proxy) for more details.

@@

\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species' interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2010]. 
Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
Indeed, we found strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing the weakest interactions (Supporting Information Section \@ref(S-undersampling)). 
Despite removing rare interactions and species, the relative size of the minimum driver-node set, the superior species, and the relative rankings of control capacity were generally maintained. Of particular note, we found that critical species in the full network were also critical in the vast majority of rarefied networks.

### 2019-01-13 paper/supp-info.Rmd
Update neeman reference (it said it was 2009 but in reality it is 2010)

Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006]. 
Nevertheless, visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependences of plants on animals and vice versa [@alarcon_congruence_2010; @king_why_2013]. 
We, therefore, investigated the effect of calculating the dependences using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success.
We did this by comparing *(i)* the size of the minimum driver node set $n_D$ of the community, *(ii)* the species' control capacity and, *(iii)* the species' probability of being a superior node. 
To do this, we used data collected by @ballantyne_constructing_2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
First, deposition networks were quantified using the mean single visit deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@neeman_framework_2009; @king_why_2013; @ballantyne_constructing_2015]. 
Second, visitation networks were constructed by counting the visits to flowers during Single Visit Depositions. 
Finally, pollinator importance networks were constructed as the product of pollinator efficiency and visit frequency.

>>>>

Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006]. 
Nevertheless, visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependences of plants on animals and vice versa [@alarcon_congruence_2010; @king_why_2013]. 
We, therefore, investigated the effect of calculating the dependences using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success.
We did this by comparing *(i)* the size of the minimum driver node set $n_D$ of the community, *(ii)* the species' control capacity and, *(iii)* the species' probability of being a superior node. 
To do this, we used data collected by @ballantyne_constructing_2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
First, deposition networks were quantified using the mean single visit deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@neeman_framework_2010; @king_why_2013; @ballantyne_constructing_2015]. 
Second, visitation networks were constructed by counting the visits to flowers during Single Visit Depositions. 
Finally, pollinator importance networks were constructed as the product of pollinator efficiency and visit frequency.
